An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-09-28 poly-embed-journal/poly-embed-journal.tex
Pass on Appendix C

\begin{definition}[Face, facet]
  Let $P \subseteq \reals^d$ be a convex polytope.
  A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
  % A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
  A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
  \begin{equation*}
    F_{(w,b)} = P \cap H_{(w,b)}~,~
  \end{equation*}
  for any valid halfspace $H^+_{(w,b)}$.
  The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
  A face $F$ with $\dim(F) = \dim(P) - 1$ is called a facet.
\end{definition}

@@

\subsubsection{Notation}
Within this appendix, we use some self-contained notation.
First, for a fixed $g$ as above, define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.

We define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$ define a halfspace for some $v \in \V$.
Similarly, we denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$; the latter will help us restrict our hypograph to the nonnegative orthant. 
Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{([e_y;0], 0)}$.

Finally, we define the face generated by $v \in \V$ with $F_v := H_v \cap G$ for any $v\in\V$.
Finally, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.

\subsection{Constructing a unique minimum set of facets from a finitely generated polyhedron}\label{appsubsec:phase1}
We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$ throughout, and let $d := |\Y|+1$.
Suppose we have a finite set $\V \subset \reals_+^\Y \times \reals$.

\begin{definition}
  Define the function $g : \reals_+^\Y \to \reals_+$ by
  \begin{align*}
    g(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
  \end{align*}
\end{definition}

@@

\begin{lemma}\label{lem:G-unique-facets-Hstar}
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
  Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet.
\end{lemma}
\begin{proof}
  Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
\end{proof}

@@

\begin{claim}\label{claim:unique-set-loss-vectors-defining-facets}
  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  Moreover, $F_v$ is a facet of $G$ for each $v\in\V^*$.
\end{claim}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.

  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
\end{proof}

@@

@@

Suppose $L$ is a minimizable loss function.
For $x\in\reals^\Y_+$, consider $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$ polyhedral.
Throughout, suppose $g(x) = \risk{L}_+(x)$.
As before, take $G$ to be the hypograph of $g$.
We define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.  
Now let $\H = \H_\Y \cup \H_{\V}$; again, this may be infinitely generated.
\begin{claim}
	$G = \cap\H$.
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in G
	&\iff g(x) \geq c & \text{ since $G$ is the hypograph of $g$}\\
	&\iff \risk L_+(x) \geq c & \text{ as $g=\risk L_+$}\\
	&\iff \inprod{v}{x} \geq c \,\, \forall v \in \V & \text{By def of $\risk L_+$ as the infimum over $v \in \V$ of}\\
	& & \text{the inner product with $x$ and minimizable.} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \text{By definition of each halfspace}\\
	&\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$} \\ 
	\end{align*}
	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $G = \cap \H$.

@@

\begin{claim}
	$\H_{\V^*} \subseteq \H$
\end{claim}
\begin{proof}
	Observe that it is not immediately clear that $\H_{\V^*} \subseteq \H$, since $\H$ is not finite, and therefore does not immediately form a halfspace representation for $G$.
	If there was a $v^* \in \V^*$ such that $H^+_{v^*} \not \in \H$, then as $\V^*$ generates facets, the projection $\pi(F_{v^*})$ has nonempty interior.
	Fix  $x \in \inter(\pi(F_{v^*}))$; we know $(x,g(x))$ supports $H_v$ at $x$ by Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
	Since $L$ is minimizable, we have $\risk L_+ = \min_{v \in \V}\inprod{v}{x} = g(x)$.
	However, since $F_{v^*}$ is a facet \jessie{ref}, it is unique, so $\argmin_{v \in \V^*}\inprod{v}{x} = \{v^*\}$ and there can be no $v' \in \V^*$ such that $F_{v'}$ supports $G$ at $x$.
	That is to say that $v^* \not \in \V$, we then contradict the fact that $L$ is minimizable.
	Thus, we must have $\H_{v^*} \subseteq \H$.
\end{proof}

@@

\subsection{Projecting from $G$ to $g$}
We now consider projections from $\reals^\Y_+ \times \reals$ onto the positive orthant $\reals^\Y_+$.

@@

Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.

\begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
  $\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
\end{corollary}

@@

  (4) $x \in \pi(F_v)$
\end{lemma}
\begin{proof}
  \begin{align*}
    (x,g(x)) \in F_v
    &\iff (x,g(x)) \in \{(x',c) \in G \mid \inprod{v}{x'} = c\}\\
    &\iff  \inprod{v}{x} = g(x)\\
    &\iff \inprod{v}{x} = \min_{v' \in \V}\inprod{v'}{x}\\
    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}
  \end{align*}
  This covers $1 \iff 2 \iff 3$.

@@

%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
  For $\V' \subseteq \V$, we have
  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
  Would like to show
  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

@@

\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
  For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
  \btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
  By Claim~\ref{claim:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
  Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
  Thus, $\pi(F_v)$ is $|\Y|$-dimensional.
\end{proof}

Denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$
\begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
  For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$.
  \btw{$1$-homogeneous version of rep iff $\Theta$ subset of level sets generated by $\R'$.}
\end{claim}
\begin{proof}
  $\implies$
  The result follows if $\V^* \subseteq \V'$, which is exactly the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
  Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.

@@

Let $r$ be a report, and let $v = L(r)$.
As $H_{v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).

@@

  If $F_v$ is a subset of a vertical facet, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
  Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
  While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$, since $g$ is continuous on $\reals^\Y_{+}$, and determined by $\V^*$ on $\reals^\Y_{++}$.

  \jessie{Justification: $g$ is continuous on $\reals_+^\Y$, and there has to be a unique $v^*$ on $\reals^\Y_{++}$.}

@@

\begin{claim}\label{claim:exists-vstar-projected-face-subset}
  For any $v \in \V$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
  \btw{shows (7) on $\reals^\Y_+$}
\end{claim}
\begin{proof}
  This is exactly Claim~\ref{claim:vface-subset-some-vstar-face} and Corollary~\ref{cor:projected-faces-subset-projected-facet} chained together.
\end{proof}

@@

\subsection{Translating to properties: projecting the domain of $g$ to $\simplex$}

Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
\begin{claim}
	We may write $f(p) = \min_{v\in\V} \inprod{p}{v} + \delta(p \mid \simplex)$ for some finite set $\V \subset \reals^\Y_+$. %\raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
\end{claim}
\begin{proof}
  We will think of $f$ as defined $f:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f) = \simplex$.
  For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
  If $p \not \in \simplex$, then $f(p) = -\infty$ and inner products are not used to compute $F$.
  Moreover, since $f$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
	\begin{align*}
	f(p) &= h(p) - \delta(p \mid C)\\
		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
		 &= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)~.~
	\end{align*}
\end{proof}

\begin{corollary}\label{cor:f-matches-g-on-simplex}
  For all concave $f : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f) = \simplex$, there is a polyhedral concave function $g : \reals^\Y_+ \to \reals_+$ with $\dom(g) = \reals^\Y_+$ so that $f(p) = g(p)$ for all $p \in \simplex$.
\end{corollary}
Given the function $f$, we consider $g$ to be its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in \S~\ref{appsubsec:phase1} and~\ref{appsubsec:phase2} to draw conclusions about the property $\Gamma := \prop{L}$.

@@

\begin{claim}
  For all $v \in \V$, $\theta(v) = \pi(F_v) \cap \simplex$.
\end{claim}
\begin{proof}
  % Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
  \btw{Moved previous proof outline to comment}

@@

\subsection{Proving Lemma~\ref{lem:X}}
\begin{lemma}\label{lem:g-1-homog}
	For the finite set $\V^* \subseteq \reals^\Y_+$, the function defined by $g(x) = \min_{v \in \V^*}\inprod{v}{x}$ is $1$-homogeneous.
\end{lemma}
\begin{proof}
	If $x \not \in \reals^\Y_+$, then $c g(x) = -\infty = g(cx)$ for any $c > 0$.
	If $x \in \reals^\Y_+$, then we have $g(cx) = \min_{v \in \V^*}\inprod{v}{cx} = c \min_{v \in \V^*}\inprod{v}{x} = c g(x)$ for any $c > 0$ by linearity of the inner product.
\end{proof}

>>>>

\begin{definition}[Face, facet]
  Let $P \subseteq \reals^d$ be a convex polyhedron.
  A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
  % A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
  A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
  \begin{equation*}
    F_{(w,b)} = P \cap H_{(w,b)}~,~
  \end{equation*}
  for any valid halfspace $H^+_{(w,b)}$.
  The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
  A face $F$ with $\dim(F) = \dim(P) - 1$ is called a facet.
\end{definition}

@@

\subsubsection{Notation}
Within this appendix, we use some self-contained notation.
We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$ throughout, and let $d := |\Y|+1$.
For a fixed concave function $g : \reals^\Y_+ \to \reals_+$, define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.

If $g$ takes the form of Definition~\ref{def:g-finite} below, define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$ define a halfspace for some $v \in \V$.
Similarly, we denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$; the latter will help us restrict our hypograph to the nonnegative orthant. 
Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y := H_{([e_y;0], 0)}$.

Finally, we define the face generated by $v \in \V$ with $F_v := H_v \cap G$ for any $v\in\V$.
Finally, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$, $\H = \H_{\V} \cup \H_\Y$.

\subsection{Constructing a unique minimum set of facets from a finitely generated polyhedron}\label{appsubsec:phase1}
Suppose we have a finite set $\V \subset \reals_+^\Y \times \reals$.
Throughout, we will work with a function $g$ generated by $\V$ of the following form.

\begin{definition}\label{def:g-finite}
  Define the function $g : \reals_+^\Y \to \reals_+$ by
  \begin{align*}
    g(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
  \end{align*}
\end{definition}

@@

\begin{lemma}\label{lem:G-unique-facets-Hstar}
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
  Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet.
\end{lemma}
\begin{proof}
  Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
\end{proof}
We can also show that the set $\H_\Y$ is contained in $\H^*$ so that we can separate the facets generated by $\H^*$ into a partition of vertical and non-vertical facets of $G$.

@@

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  Moreover, $F_v$ is a facet of $G$ for each $v\in\V^*$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.
  Take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ to be the unique set generating $\H_{\V^*}$.
  (Uniqueness of $\V^*$ follows from uniqueness of $\H^*$.)
  The moreover follows since every $H_v \in \H_{\V^*} \subseteq \H^*$ generates a facet.

%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
\end{proof}

@@

This series of results will let us reason about the Bayes risk (and $1$-homogeneous extension) of losses with finite representative sets in \S~\ref{subsec:lem-X-proof}.

@@

Suppose $L$ is a minimizable loss function.
For $x\in\reals^\Y_+$, consider the $1$-homogeneous extension of Bayes risk  $\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$ polyhedral.
Throughout, suppose $g(x) = \risk{L}_+(x)$.
As before, take $G$ to be the hypograph of $g$.
We define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.  
Now let $\H = \H_\Y \cup \H_{\V}$; again, this may be infinitely generated.
\begin{claim}
	$G = \cap\H$.
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in G
	&\iff g(x) \geq c & \text{ since $G$ is the hypograph of $g$}\\
	&\iff \risk L_+(x) \geq c & \text{ as $g=\risk L_+$}\\
	&\iff \inprod{v}{x} \geq c \,\, \forall v \in \V & \text{By def of $\risk L_+$ as the infimum over $v \in \V$ of}\\
	& & \text{the inner product with $x$ and minimizable.} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in L(\R) & \text{By definition of each halfspace}\\
	&\iff (x,c) \in \cap \H_\V & \text{Since true for all $v \in \V$} \\ 
	\end{align*}
	Combining the two equalities (e.g., $\cap \H = (\cap \H_\Y) \cap (\cap \H_\V)$), we have $G = \cap \H$.

@@

\jessiet{Commented out claim that has no label, so is not being explicitly used later, please double check that we don't use it.  The proof has some forward refs}
%\begin{claim}
%	$\H_{\V^*} \subseteq \H$
%\end{claim}
%\begin{proof}
%	Observe that it is not immediately clear that $\H_{\V^*} \subseteq \H$, since $\H$ is not finite, and therefore does not immediately form a halfspace representation for $G$.
%	If there was a $v^* \in \V^*$ such that $H^+_{v^*} \not \in \H$, then as $\V^*$ generates facets, the projection $\pi(F_{v^*})$ has nonempty interior.
%	\jessiet{Originally moved this subsection down because this uses the projection $\pi$, but it seems like the best solution might be to move $\pi$ and loss notation into the very first subsection.  Or re-work this proof.}
%	Fix  $x \in \inter(\pi(F_{v^*}))$; we know $(x,g(x))$ supports $H_v$ at $x$ by Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
%	Since $L$ is minimizable, we have $\risk L_+(x) = \min_{v \in \V}\inprod{v}{x} = g(x)$.
%	However, since $F_{v^*}$ is a facet of $G$ (Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}), it is unique, we have $\argmin_{v \in \V^*}\inprod{v}{x} = \{v^*\}$ and there can be no $v' \in \V \setminus \V^*$ such that $F_{v'}$ supports $G$ at $x$.
%	%That is to say that $v^* \not \in \V$, we then contradict the fact that $L$ is minimizable.
%	Thus, we must have $\H_{v^*} \subseteq \H$.
%\end{proof}

@@

\subsection{Projecting from $G$ to $g$}\label{subsec:project-pi}
We now consider projections from $\reals^\Y_+ \times \reals$ onto the positive orthant $\reals^\Y_+$.

@@

Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
This projected faces generated by $\V^*$ covers the nonnegative orthant.
\begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
	$\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
\end{corollary}

Moreover, the projection $\pi$ preserves dimension of faces.

@@

	(4) $x \in \pi(F_v)$
\end{lemma}
\begin{proof}
	\begin{align*}
	(1) (x,g(x)) \in F_v
	&\iff (x,g(x)) \in \{(x',c) \in G \mid \inprod{v}{x'} = c\} & \\
	&\iff  \inprod{v}{x} = g(x) & (2)\\
	&\iff \inprod{v}{x} = \min_{v' \in \V}\inprod{v'}{x} & \\
	&\iff v \in \argmin_{v' \in \V}\inprod{v'}{x} & (3)
	\end{align*}
	This covers $1 \iff 2 \iff 3$.

@@

Now we can observe a set of normals generating facets whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
	For $\V' \subseteq \V$, we have
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
	We would like to show
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

@@

For the set $\V^*$, we have each of these projected facets being full-dimensional in the projected space as well.
\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
	Thus, $\dim(F_v) = \dim(\pi(F_v)) = |\Y|$.
\end{proof}

Denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$ as the set of projected facets generated by $\V^*$.

\begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
	Suppose we are given a minimizable loss $L$ will polyhedral extended Bayes risk $\risk{L}_+(x) := \inf_{r \in \R} \inprod{x}{L(r)}$.
	Take $\R' \subseteq \R$ with $\V' := L(\R')$. \jessiet{Added this in since I re-organized subsections, but I don't think we want this notation isolated to this claim.}
	For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$.
	\btw{$1$-homogeneous version of rep iff $\Theta$ subset of level sets generated by $\R'$.}
\end{claim}
\begin{proof}
	$\implies$
	The result follows if $\V^* \subseteq \V'$, which is exactly the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.

@@

Given a loss $L$ with $\risk L_+$ polyhedral, take $v = L(r)$ for any $r \in \R$.
As $H_{v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).

@@

	If $F_v$ is a subset of a vertical facet $F_y$, we would have $F_v = H_v \cap G \subseteq H_y \cap G$ for some $y \in \Y$.
	Expanding, this is $\{(x,g(x)) \mid \inprod{v}{x} = g(x)\} \subseteq \{(x,g(x)) \mid x_y = 0 \}$.
	While this can happen, it must be on the boundary of $\reals_+^d$, and must be at the intersection of $H_y$ and some other $H_{v^*}$ for $v^* \in \V^*$, since $g$ is continuous on $\reals^\Y_{+}$, and determined by $\V^*$ on $\reals^\Y_{++}$.
	\jessiet{Justification: $g$ is continuous on $\reals_+^\Y$, and there has to be a unique $v^*$ on $\reals^\Y_{++}$. More hand-wavy than I'd like}
\end{proof}

@@

Now, we can conclude that projected facets generated by $\V$ contain all other projected faces of $G$.
\begin{corollary}\label{cor:exists-vstar-projected-face-subset}
	For any $v \in \V$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
	\btw{shows (7) on $\reals^\Y_+$}
\end{corollary}
\begin{proof}
	This is exactly Claim~\ref{claim:vface-subset-some-vstar-face} and Corollary~\ref{cor:projected-faces-subset-projected-facet} chained together.
\end{proof}

@@

\subsection{Translating to properties: projecting from $\reals^\Y_+$ to $\simplex$}\label{subsec:project-f}

Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
\begin{claim}
	We may write $f(p) = \min_{v\in\V} \inprod{p}{v} + \delta(p \mid \simplex)$ for some finite set $\V \subset \reals^\Y_+$. %\raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
\end{claim}
\begin{proof}
  We will think of $f$ as defined $f:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f) = \simplex$.
  For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
  If $p \not \in \simplex$, then $f(p) = -\infty$ and inner products are not used to compute $F$.
  Moreover, since $f$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
	\begin{align*}
	f(p) &= h(p) - \delta(p \mid C)\\
		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
		 &= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)~.~
	\end{align*}
\end{proof}
Thi allows us to project $g$ from $\reals^\Y_+$ to the simplex $\simplex$.
\begin{corollary}\label{cor:f-matches-g-on-simplex}
  For all concave $f : \reals^\Y_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f) = \simplex$, there is a polyhedral concave function $g : \reals^\Y_+ \to \reals_+$ with $\dom(g) = \reals^\Y_+$ so that $f(p) = g(p)$ for all $p \in \simplex$.
\end{corollary}
Given the function $f$, we consider $g$ to be its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in \S~\ref{appsubsec:phase1} and~\ref{appsubsec:phase2} to draw conclusions about the property $\Gamma := \prop{L}$ defined on the simplex.

@@

\begin{claim}\label{claim:theta-is-pi-cap-simplex}
  For all $v \in \V$, $\theta(v) = \pi(F_v) \cap \simplex$.
\end{claim}
\begin{proof}
  % Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
  \btw{Moved previous proof outline to comment}

@@

\subsection{Proving Lemma~\ref{lem:X}}\label{subsec:lem-X-proof}
Now that we have translated from $\reals^d_+$ to $\reals^\Y$ in \S~\ref{subsec:project-pi} and from $\reals^\Y_+$ to $\simplex$ in \S~\ref{subsec:project-f}, we can take the final steps to prove Lemma~\ref{lem:X}.
\begin{lemma}\label{lem:g-1-homog}
	For the finite set $\V^* \subseteq \reals^\Y_+$, the function defined by $g(x) = \min_{v \in \V^*}\inprod{v}{x}$ is $1$-homogeneous.
\end{lemma}
\begin{proof}
	If $x \not \in \reals^\Y_+$, then $c g(x) = -\infty = g(cx)$ for any $c > 0$.
	If $x \in \reals^\Y_+$, then we have $g(cx) = \min_{v \in \V^*}\inprod{v}{cx} = c \min_{v \in \V^*}\inprod{v}{x} = c g(x)$ for any $c > 0$ by linearity of the inner product.
\end{proof}
